---
title: "P8105_hw1_yz4186"
author: "Yunxi Zhang"
date: "9/26/2021"
output: github_document
---

```{r}
library(tidyverse)
```

# Problem 1
## This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.
### Create a data frame comprised of:
### * a random sample of size 10 from a standard Normal distribution
### * a logical vector indicating whether elements of the sample are greater than 0
### * a character vector of length 10
### * a factor vector of length 10, with 3 different factor “levels”

```{r}
prob1_df = 
  tibble(
  sample = rnorm(10, sd = 1, mean = 0),
  vec_logical = sample > 0,
  vec_char = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor = c(factor("A", "B", "C"))
)

prob1_df

```

### Try to take the mean of each variable in your dataframe. What works and what doesn’t?
### Hint: to take the mean of a variable in a dataframe, you need to pull the variable out of the dataframe. Try loading the tidyverse and using the pull function.

```{r, warning = FALSE}
mean(pull(prob1_df, sample))
mean(pull(prob1_df, vec_logical))
mean(pull(prob1_df, vec_char))
mean(pull(prob1_df, vec_factor))
```
The random sample and logical vector work. The character vector and factor verctor don't work. 


### In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

```{r, warning = FALSE}
as.numeric(pull(prob1_df, vec_logical))
as.numeric(pull(prob1_df, vec_char))
as.numeric(pull(prob1_df, vec_factor))
```
When we tried to use "as.numeric" function to test those variables being interpretable as numbers I found that only the logical vector can be interpreted as number, both characteristic and factor vectors cannot be interpreted as number. The "mean" function only works for number. So, that's why we can't calculated the mean of them in the previous problem.


## Problem 2
### This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.

### Use the code below to download the a package containing the penguins dataset:

## install.packages("palmerpenguins")

### (Note – you only need to run this command once to install the package, and you can do so directly in the console. This code shouldn’t be executed by your RMarkdown file.)

### Next, use the following code (in your RMarkdown file) to load the penguins dataset:

```{r}
data("penguins", package = "palmerpenguins")
```

### Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:

### the data in this dataset, including names / values of important variables
### the size of the dataset (using nrow and ncol)
### the mean flipper length


The data including variable names: `r names(penguins)` , and 
`r nrow(penguins)` rows, `r ncol(penguins)` columns, the mean of flipper_length_mm is `r mean(penguins$flipper_length_mm, na.rm = T)`. 


## Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).

```{r, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point(aes(color=species))
```

## Export your first scatterplot to your project directory using ggsave.

```{r, warning = FALSE}
ggsave("hw1_plot.pdf", height = 4, width = 6)
```









